### 2008-02-25 htdocs/sections.tex
Added information on solid wall options
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@187 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.1 2008-02-04 12:46:14 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In parallel, this sets the processor Cartesian decomposition, i.e.,
the number of processors in each dimension of the Cartesian communicator.
The default value may be implementation dependent as it is that returned
by \texttt{MPI\_Dims\_create()}. For
example:
\begin{verbatim}
size 64_64_64
grid 4_2_1
\end{verbatim}
gives a total (physical) system size of 64 lattice sites in each
direction, decomposed across 4 processors in the x-direction, 2 in
the y-direction and 1 (no decomposition) in the z-direction. The
total number of processors must therefore be 8. The local domain
size per processor is then 16x32x64.

@@

\subsection{Input/Output}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.2 2008-02-25 09:53:37 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In parallel, this sets the processor Cartesian decomposition, i.e.,
the number of processors in each dimension of the Cartesian communicator.
The default value may be implementation dependent as it is that returned
by \texttt{MPI\_Dims\_create()}. For
example:
\begin{verbatim}
size 64_64_64
grid 4_2_1
\end{verbatim}
gives a total (physical) system size of 64 lattice sites in each
vdirection, decomposed across 4 processors in the x-direction, 2 in
the y-direction and 1 (no decomposition) in the z-direction. The
total number of processors must therefore be 8. The local domain
size per processor is then 16x32x64.

@@

Solid planar boundary walls can be added at the extremities of the
system (i.e., the volume of fluid is extactly that specified by
the \texttt{size} keyword). The wall can be in one, two or all three
coordinate direcctions, i.e., a 'slab' geometry, and 'duct' geometry
or a 'box' geometry, respectively.

The boundary walls are switched on via the keyword value pair

\inputkey{boundary\_walls\_on [no | yes]}

If \texttt{yes} then the geometry is specified with the keyword
as one of

\inputkey{periodicity [1\_1\_1 | 1\_1\_0 | 1\_0\_0 | 0\_0\_0]}

Note that these are the only valid selections. \texttt{1\_1\_0}
gives periodic boundaries in the $x-$ and $y-$directions, with
walls at either edge in the $z-$direction. \texttt{1\_0\_0}
gives periodic conditions in the $x-$ direction only, while
\texttt{0\_0\_0} is a fully enclosed box.

In the case of the slab geometry, two further values are used so
that shear may be imparted to the system:

\inputkey{boundary\_speed\_bottom}

\inputkey{boundary\_speed\_top}

These values set the $x-$component of the wall velocity at
$z = z_{min}$ and $z = z_{max}$, respectively. Like all
velocities, these values must respect the low Mach number
constraint $u_x < c_s$.
\subsection{Input/Output}
